
\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper, margin=.7in]{geometry}
\usepackage[compact]{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome} \hypersetup{ colorlinks=false, } \titleformat*{%
\section}{\Large\bfseries\scshape}
\pagestyle{empty}
\urlstyle{same} \setlength{\parskip}{0pt} \setlength{\parsep}{0pt}
\setlength{\headsep}{0pt} \setlength{\topskip}{0pt} \setlength{\topmargin}
{0pt} \setlength{\topsep}{0pt} \setlength{\partopsep}{0pt}
\begin{document}
\thispagestyle{empty}

\begin{center}
    \textbf{\textsc{\Huge Raghava Dhanya}} \rule{\textwidth}{.4pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%
%       social      %
%%%%%%%%%%%%%%%%%%%%%
\begin{center}
    \href{mailto:raghavadhanya@gmail.com}{\faEnvelope\ raghavadhanya@gmail.com}
    \ | \ %
    \href{tel:9148995472}{\faPhoneSquare\ 9148995472} \ | \ %
    \href{https://github.com/RaghavaDhanya}{ \underline{\faGithubSquare\
    GitHub}} \ | \ \href{https://in.linkedin.com/in/raghavadhanya}{\underline
    {\faLinkedinSquare\ LinkedIn}} \\
    Bengaluru 562157
\end{center}
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%
%     Education     %
%%%%%%%%%%%%%%%%%%%%%
\section{Education} \textbf{Bachelor of Engineering,} computer science
and engineering \hfill [\textit{2014-present}]\\
Aggregate:  \textit{75.92\%}\\
Electives:  \textit{`Pattern Recognition', `Artificial Intelligence',
`Clouds,Grids and Clusters'.}\\
\textit{Sir M. Visvesvaraya Institute of Technology,} Bengaluru
\medskip
\\
\textbf{Machine Learning} by Stanford University on Coursera.\hfill [\textit
{March 2017 - July 2017}]\\
Certificate earned on July 21,2017 
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%
%      skills       %
%%%%%%%%%%%%%%%%%%%%%
\section{Skills} Technologies:  Android, Machine Learning, Amazon Web
Services, Django, Continuous Integration.\\
Programming languages:  C/C++, Java, Python, JavaScript, SQL, Shell,
HTML \& CSS.\\
Others:  Numpy, Scipy, Git, Unix/Linux, Windows. 
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%
%    Experience     %
%%%%%%%%%%%%%%%%%%%%%
\section{Experience} \textbf{Technology Developer,} \textit{notNULL},
Bengaluru \hfill [\textit{February 2016 - July 2016}]\\
Worked on developing a verification technology for events.
\medskip
\\
\textbf{Software Development Intern,} \textit{Supertext}, Bengaluru
\hfill [\textit{August 2016 - December 2016}]\\
Developed an android app for company communication with vendors using
parse and firebase as backend. 
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%
%     Projects      %
%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\textbf{\underline{\large\href{https://github.com/abhijith0505/Tonite}
{Tonite}}}\hfill[\textit{April 2016}]
\par
Wardrobe assistant app to keep track of the clothes and gives purchase
suggestions based on events in user's calendar.  Built at Hackerramp
2016 (16th and 17th April ), Myntra office Bangalore.\\
\textit{Technologies used:  Android, Java, XML.}
\smallskip
\\
\textbf{\underline{\large\href{https://github.com/RaghavaDhanya/ReMorse}
{ReMorse}}}\hfill[\textit{April 2017}]
\par
A 2D side scrolling game which tries to subconsciously teach Morse Code.\\
\textit{Technologies used:  C++, OpenGL, Box2D}
\smallskip
\\
\textbf{\underline{\large\href{https://github.com/RaghavaDhanya/Codesnap}
{Codesnap}}}\hfill[\textit{August 2016}]
\par
A chrome extension which adds copy button to code segments in most
websites, also provides a code clipboard history.\\
\textit{Technologies used:  Chrome developer tools, JavaScript, CSS,
HTML.  }
\smallskip
\\
\textbf{\underline{\large\href{https://github.com/RaghavaDhanya/FileHide}
{FileHide}}}\hfill[\textit{May 2016}]
\par
A cross platform app which hides one file in another, the host will
still work normally.  This application hides a given file like pdf,
video or image in another file like pdf, video or image.\\
\textit{Technologies used:  Python, Tkinter.}
\smallskip
\\
\textbf{\underline{\large\href{https://github.com/RaghavaDhanya/Snake}
{Snake}}}\hfill[\textit{December 2015}]
\par
Simple, classic and cross platform snake game.\\
\textit{Technologies used:  Python, Pygame.} 
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Activities & Interests %
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activities and Interests}
\begin{itemize}
        \itemsep0em
    \item
        Currently enrolled in Deep Learning and Neural Networks by
        deeplearning.ai on Coursera.
    \item
        Competitive coding, Volunteered for android app development for
        college fest Kalanjali-2015.
    \item
        Twice second place in coding and debugging conducted during
        college fest.
    \item
        Lance corporal, National Cadet Corps – Air Wing (High school)
    \item
        Graphic designing, designed many posters and banners for college
        events
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

